Neural Models for Target-Based Computer-Assisted Musical Orchestration: A Preliminary Study

### 2020-08-19 paper/aimusic2020/paper.tex
Fix small typos

The second and more deep model that we trained as classifier was the well known deep residual network \emph{ResNet}. Specifically, we used 18-layer ResNet, which allows information to pass directly from the input to the final layer of each block. Besides, to make the model more suitable to our problem, we decided to reduce the number of parameters and to reset the output channel numbers of each block with 32, 64, 32, 32 respectively.

@@

In order to have a more fair comparison, we did not allow Orchidea to use any of the advanced features: we did not apply any symbolic constraints or harmonic analysis and we forced it forced to use all 10 instruments in each solution. This creates a more fair comparison, since our models are unable to create constrained or sparse solutions.

>>>>

The second and deeper model that we trained as classifier was the well known deep residual network \emph{ResNet}. Specifically, we used 18-layer ResNet, which allows information to pass directly from the input to the final layer of each block. Besides, to make the model more suitable to our problem, we decided to reduce the number of parameters and to reset the output channel numbers of each block with 32, 64, 32, 32 respectively.

@@

In order to have a fairer comparison, we did not allow Orchidea to use any of the advanced features: we did not apply any symbolic constraints or harmonic analysis and we forced it forced to use all 10 instruments in each solution. This creates a more fair comparison, since our models are unable to create constrained or sparse solutions.
